### 2019-04-15 manuscript.tex
Autocommit (fgc)
Update manuscript.tex

Only women with daughters to be considered for FGC were included in the main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}. “alternative convention/peer convention\cite{ShelWand11}
 \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.  \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}
\cite{PashPonn16}: Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms

@@

>>>>

Only women with daughters to be considered for FGC were included in 
 main model (the daughter model) and the future-daughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\cfcmt{FGC module at \url{https://dhsprogram.com/pubs/pdf/DHSQMP/DHS5_Module_Female_Genital_Cutting.pdf}}

@@

- conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} vs. 
- “attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}. “alternative convention/peer convention\cite{ShelWand11}
 \cite{ShelWand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.  \cfonly{Mackie's social convention theory was supported in \cite{ShelWand11}.  In \cite{MackLeJe08}, the authors saw marriageability was only one reason for FGC and proposed multiple factors in influencing women’s decision of cutting their daughters.

\cite{PashPonn16}: Attitude was the strongest predictor of mothers' intentions for their daughters' FGC status, followed by subjective norms

@@

What does it mean that group level of daughter future as the biggest predictor compared to individual benefit and group fgc (prevalence)?  Does it mean that fgc norm works implicitly and it might not be something behaviour women really agree with?  Is it a social norm supported by social sanction (i.e., cutting daughter) for what reason? (see \cite{MackLeJe08} (p.28 which mentioned Bicchieri06)
